Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)

### 2024-11-29 paper/paper.qmd
Delete unused scripts

---
title: "Understanding Factors Contributing to Application Approval in Urban Planning Decisions"
subtitle: "Analysis using data from Toronto’s Committee of Adjustment applications leveraging Bayesian Logistic Regression"
author: Angel Xu
thanks: "Code and data are available at: [https://github.com/Anjojoo/Committee-of-Adjustment-Applications](https://github.com/Anjojoo/Committee-of-Adjustment-Applications)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The analysis presented in this paper were conducted using R programming language [@citeR]. The `tidyverse` packages [@citetidyverse], `dplyr` package [@citedplyr], and `arrow` package [@citearrow] were used in the process of data simulation, testing beforehand. After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], and `dplyr` package [@citedplyr], data cleaning process was done by using `tidyverse` package [@citetidyverse], `dplyr` package [@citedplyr], and `arrow` package [@citearrow]. The code style is corrected by `here` package [@citehere], `lintr` package [@citelintr], and `styler` package [@citestyler]. Then, models were constructed using `tidyverse` package [@citetidyverse], and `rstanarm` [@citerstanarm] package. Model validation utilizes `Metrics` package [@citeMetrics] Graphs were made with `ggplot2` package [@citeggplot]. Tables were constructed with `knitr` package [@citeknitr]. The model results are then presented by `modelsummary` [@citemodelsummary] package.

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm and `Metrics` package of @citeMetrics. `rstanarm`@rstanarm is used to set up the model, and `Metrics` @citeMetrics is used to calculate RMSE.

@@

2. **Predictive Accuracy (RMSE)**

The Root Mean Square (RMSE) typically measures the deviation between predicted values and observed values in the same metric. In the case of a logistic regression model predicting probabilities ($p_i$), the observed outcomes ($y_i$) are binary, which means they aren’t directly comparable in the usual sense of residuals as continuous values. However, RMSE can still be used as a measure of predictive performance for logistic regression by interpreting as the observed realization of the probabilities.

Logistic regression models the probability of an event occurring, $\hat{p_i}=P(y_i=1)$ while The observed binary outcome (y_i) is an approximation of whether the event occurred (1) or not (0). The squared error between the predicted probability and the binary outcome measures how well the model assigns probabilities close to the actual outcome. Thus, the equation of the Squared Error is :

$$Squared \: Error = (y_i-\hat{p_{i}})^2$$

RMSE aggregates this squared error across all observations and provides a measure of how well the model predicts probabilities in line with the observed binary outcomes. Consequently, the RMSE equation is:

$$RMSE = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(y_{i}-\hat{p_{i}})^2}$$

#### Workspace setup ####
library(Metrics) # For RMSE calculation
library(rstanarm)

#### Read the model
model <-
  readRDS(file = here::here("models/first_model.rds"))

#### Generate predictions ####
# Predicted probabilities
predicted_probabilities <- posterior_predict(model, draws = 1) %>% 
  as.vector()

# RMSE Calculation
rmse_value <- rmse(analysis_data$decision, predicted_probabilities)

#### Print RMSE ####
print(paste("RMSE:", rmse_value))
```

A low RMSE indicates that the predicted probabilities are close to the observed outcomes, demonstrating good predictive accuracy.

@@

@@

@@

>>>>

---
title: "Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)"
subtitle: "Analysis using data from Toronto’s Committee of Adjustment applications using Bayesian Logistic Regression"
author: Angel Xu
thanks: "Code and data are available at: [https://github.com/Anjojoo/Committee-of-Adjustment-Applications](https://github.com/Anjojoo/Committee-of-Adjustment-Applications)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The analysis presented in this paper were conducted using R programming language [@citeR]. The `tidyverse` packages [@citetidyverse], `dplyr` package [@citedplyr], and `arrow` package [@citearrow] were used in the process of data simulation, testing beforehand. After the original raw data was downloaded by using `tidyverse` package [@citetidyverse], and `dplyr` package [@citedplyr], data cleaning process was done by using `tidyverse` package [@citetidyverse], `dplyr` package [@citedplyr], and `arrow` package [@citearrow]. The code style is corrected by `here` package [@citehere], `lintr` package [@citelintr], and `styler` package [@citestyler]. Then, models were constructed using `tidyverse` package [@citetidyverse], and `rstanarm` [@citerstanarm] package. Graphs were made with `ggplot2` package [@citeggplot]. Tables were constructed with `knitr` package [@citeknitr]. The model results are then presented by `modelsummary` [@citemodelsummary] package.

@@

We run the model in R [@citeR] using the `rstanarm` package of @citerstanarm. `rstanarm`@citerstanarm is used to set up the model.

@@

2. Confusion Metrix

@@

library(rstanarm)

model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

model <- model

@@

### Overview
This appendix delves into the methodological considerations underlying the data used in this paper, focusing on the challenges and intricacies of observational data, the implications of sampling, and the potential use of surveys and simulations to enrich insights.

### Methodology

### Sampling Approach

#### Target Population

#### Sampling Frame

#### Trade-offs

### Idealized Methodology

### Survey
